\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2021-10-15 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.Rmd
version sent to Jim and Olli

We would like to thank the anonymous reviewers for their insightful comments and criticisms. We would also like to thank Yi Yang for helpful discussions on penalized regression models. \mbox{Bhatnagar} gratefully acknowledges funding via a Discovery Grant from the Natural Sciences and Engineering Research Council of Canada (NSERC).

>>>>

We would like to thank the anonymous reviewers for their insightful comments and criticisms. We would also like to thank Yi Yang for helpful discussions on penalized regression models. \mbox{Bhatnagar} gratefully acknowledges funding via a Discovery Grant from the Natural Sciences and Engineering Research Council of Canada (NSERC), RGPIN-2020-05133.
